# Other Programs in the US {-#other-programs-in-the-us}

After this 1st cohort graduates it will be clear to the rest of the world that MBAn at Michigan is the #1 program in the country (GO BLUE)! Until then, we'll have to rely on data from other schools whose programs are similar.  The list below is not exhaustive, but it includes those who have prestige and recognition similar to UofM.  

The rankings for the MBA programs help gauge the overall prestige and difficulty of the business school.  Those rankings come from [US News 2023 Report](https://www.usnews.com/best-graduate-schools/top-business-schools).  The MBAn rankings come from the [QS World University 2022 Report](https://www.topuniversities.com/university-rankings/business-masters-rankings/business-analytics/2022).


***

```{r include=FALSE}
library(readr)
library(knitr)
library(bs4cards)
library(bsplus)
Other_Programs <- read_csv("assets/Other Programs.csv")
```


```{r include=FALSE}
out = NULL
schools = Other_Programs$School
for (school in schools){
  school_data = Other_Programs[Other_Programs$School==school,]
  out = c(out,knit_expand('templates/other_program_template.rmd'))
}
```
`r paste(knit(text = out), collapse = '\n')`

