

```{r include=FALSE}
library(readr)
library(knitr)
Job_Postings <- read_csv("assets/Job Postings.csv")
```



# Possible Careers {-#possible-careers}

High level summary

## Data Scientist {-#data-scientist}

Bryant is doing this part!

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Scientist',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```


## Data Engineer {-#data-engineer}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Engineer',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```

## Business Analyst {-#business-analyst}

Mathis is doing it 



```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Business Analyst',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```


## Data Analyst {-#data-analyst}

Chaoyi is doing it

> Summary of role

Data Analyst is responsible for collecting, storing, and processing a large number of data by scientific priciples and technical experitise to do analysis, make proper decisions, and provide high-quality service for customers. Although it is something similar with business analyst, Data Analyst is more focused on developing technical skills and using data management and machine learning to construct data structure and dive into data to solve problems for companies. Therefore, Data Analyst should be strongly sensitive in mining data and discovering the numerical value.

> Salary

Here is the overall career path and salary of each path of a Data Analysis, and all salaries shown are medium:

1. Data Analyst (0-1 years): $62,382

2. Senior Data Analyst (2-4 years): $95,304

3. Senior Data Analyst IV (5-7 years): $128,321

4. Principal Data Analyst (8+ years): $143,837

Resource: Glassdoor

> Companies

* Retail: Amazon, Walmart, Target, Costco Wholesale, Home Depot

* Technology: Microsoft, Apple, Dell, Intel, Alphabet

* Business Services: Paypal Holdings, Visa, Mastercard, ManpowerGroup, WasteManagement

* Financials: Berkshire Hathaway, J.P.Morgan Chase, Bank of America, Wells Fargo, Citigroup

Category standard: Fortune 500

>Skills required

* Master or above degree in Computer Science, Information Management, Data Analysis, and other related.

* Proficient at least one in Java, C++, SQL, Python, R, and other programming language.

* Proficient at least one in Tableau, Domo, Power BI, and other visualization tools.

* Sensitivity in data mining, processing, and presenting, and willingness to learn new and advanced technical analysis methods.

* Highly analytical skills that could define problems, collect necessary data, establish facts, and provide reasonable recommendations for clients.

* Solid team-working and multi-task skills that you could handle relationships between different team members and deal with various kinds of problems with great flexibility.

* Prior working and internship experience in researchers, analyst, and information technology is preferred.

> Open roles on LinkedIn

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Analyst',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```

## Business Intelligence Engineer {-#business-intelligence-engineer}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Business Intelligence Engineer',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```
