

```{r include=FALSE}
library(readr)
library(knitr)
Job_Postings <- read_csv("assets/Job Postings.csv")
```



# Possible Careers {-#possible-careers}

High level summary

## Data Scientist {-#data-scientist}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

```{r echo=FALSE}
# kable(Job_Postings[Job_Postings$Role=='Data Scientist',])
Job_Postings %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )

```


## Quantitative Analyst {-#quantitative-analyst}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

## Data Quality Analyst {-#data-quality-analyst}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn


## Associate Consultant {-#associate-consultant}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn


## Product Analyst {-#product-analyst}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

## Data Analyst {-#data-analyst}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

## Data Engineer {-#data-engineer}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

## Business Analyst {-#business-analyst}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn


