

```{r include=FALSE}
library(readr)
library(knitr)
Job_Postings <- read_csv("assets/Job Postings.csv")
```



# Possible Careers {-#possible-careers}

High level summary

## Data Scientist {-#data-scientist}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Scientist',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```


## Data Engineer {-#data-engineer}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Engineer',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```

## Business Analyst {-#business-analyst}

Mathis is doing it 



```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Business Analyst',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```


## Data Analyst {-#data-analyst}

Chaoyi is doing it


```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Analyst',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```

## Business Intelligence Engineer {-#business-intelligence-engineer}

Summary of role
Salary
Companies
Skills required
Open roles on LinkedIn

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Business Intelligence Engineer',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```
