--- 
site: bookdown::bookdown_site
title: "MBAn Career Pulse"
author: "007 Wolverines"
documentclass: book
favicon: images/favicon.ico
description: |
  MBAn Career Pulse
---


```{r include=FALSE}
# libraries to include
library(bs4cards)
```



# Intro {-#intro}

Welcome to the MBAn Career Pulse site! This site will serve as a comprehensive guide on the exciting job market that awaits our inaugural class of MBAn students.  We're hoping that you'll be able to better understand how data is the "heartbeat" that drives all business through using our Pulse site.

## MBAn at Michigan {-#mban-at-michigan}

Our cohort of 52 students has a diverse background and set of skills and we are gaining a foundation in both data analytics and business management through this program.  After completing the 10-month, full-time residential program we'll have many options to choose from when it comes to our desired career paths.  We'll cover a few interesting ones and expand on their salary expectations as well as companies or cities we might end up in.

<!--chapter:end:index.Rmd-->

# Other Programs in the US {-#other-programs-in-the-us}

After this 1st cohort graduates it will be clear to the rest of the world that MBAn at Michigan is the #1 program in the country (GO BLUE)! Until then, we'll have to rely on data from other schools whose programs are similar.  The list below is not exhaustive, but it includes those who have prestige and recognition similar to UofM.  


***

```{r include=FALSE}
library(readr)
library(knitr)
library(bs4cards)
Other_Programs <- read_csv("assets/Other Programs.csv")
```



```{r include=FALSE}
out = NULL
schools = Other_Programs$School
for (school in schools){
  school_data = Other_Programs[Other_Programs$School==school,]
  out = c(out,knit_expand('templates/other_program_template.rmd'))
}
```
`r paste(knit(text = out), collapse = '\n')`


<!--chapter:end:01-OtherPrograms.Rmd-->

# Salary Expectations {-#salary-expectations}

Use data from other schools

<!--chapter:end:02-SalaryExpectations.Rmd-->



```{r include=FALSE}
library(readr)
library(knitr)
Job_Postings <- read_csv("assets/Job Postings.csv")
```



# Possible Careers {-#possible-careers}

An MBAn program helps build a foundation in both data analytics and business management.  The careers detailed below are primarly data orientated and many of the Ross MBAn graduates will end up in these roles or similar ones.  This list is not exhaustive, but provides good insight on a few popular career paths and their salary expectations and possible companies.

## Data Scientist {-#data-scientist}

**Summary of role**

Data scientists work closely with business stakeholders to understand their goals and determine how data can be used to achieve those goals. They design data modeling processes, create algorithms and predictive models to extract the data the business needs, and help analyze the data and share insights with peers. 

While data analysts typically work with structured data to solve tangible business problems, data scientists often deal with the unknown by using more advanced data techniques to make predictions about the future. This role is generally considered a more advanced version of a data analyst.

**Salary**

According to [Indeed](https://www.indeed.com/career/data-scientist/salaries), the average salary for a data scientist is $141,059 per year in the United States.
Also according to [Glassdoor](https://www.glassdoor.com/Salaries/data-scientist-salary-SRCH_KO0,14.htm), the estimated total pay for a data scientist is $120,206 per year in the United States area, with a base pay of $99,548 plus $20,657 additional pay. Additional pay could include cash bonus, commission, tips, and profit sharing. The total pay ranges between 90K to 172K. 

**Preferred Skills**

* BS/MS in quantitative field (Computer Science, Statistics, Mathematics, Analytics, Data Science)
* Proficient in data analysis tools and programming languages such as SQL, Python or R
* Experience in building visualizations (using Tableau/Qlik Sense/Excel/R/Python/tool of choice)
* Good working knowledge of cloud based services

**Open roles on LinkedIn**

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Scientist',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```


## Data Engineer {-#data-engineer}

**Summary of role**

A data engineer mainly focuses on organizing data for companies’ analytical tasks. Data Engineer are often in charge of constructing data pipelines to combine data from various source systems. They prepare the data for use in analytics applications by integrating, consolidating, and cleaning it; improving their organization's big data environment and making data easily accessible.

The quantity of data a data engineer uses depends on the organization, especially in terms of size. The analytics architecture will be increasingly complicated and the engineer will be in charge of more data as the organization gets bigger. Data-intensive industries include healthcare, retail, and financial services etc.

**Salary**

From 0 – 1 years of experience, the total pay ranges from $82k to $187k per year. The estimated total pay for a data engineer is $114,993 per year in the United States, with an average salary of $89,540 per year plus $25,452/yr additional pay. Additional pay could include cash bonus, commission, tips, and profit sharing.

**Skills required**

Some of the primary functions of a data engineer include things like developing data collection processes, integrating new software and data management technologies into an existing system and streamlining the existing foundational processes for data collection and use. Therefore, it requires:

* Programming in a least one language (Python, Java, SAS, R, MatLab, C, C++, etc.)
* Data warehousing: familiarity and experience using data warehousing solutions.
* Knowledge of operating systems: intimate understanding of operating systems, such as: Apple macOS, Microsoft Windows, Linux, Solaris and UNIX  
* Database systems: deep understanding of database management, such as SQL which is considered the most widely used solution  

**Open roles on LinkedIn**

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Engineer',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```

## Business Analyst {-#business-analyst}

**Summary of role**

Business analysts are responsible for bridging the gap between IT and the business using data analytics to assess processes, determine requirements and deliver data-driven recommendations and reports to executives and stakeholders. 
Business analysts engage with business leaders and users to understand how data-driven changes to process, products, services, software, and hardware can improve efficiency and add value. They must articulate those ideas but also balance them against what’s technologically feasible and financially and functionally reasonable. 

Being a business analyst is usually considered a great career because it offers strong salaries, plentiful job opportunities, and they generally report high job satisfaction and work-life balance. The possibilities are endless in a career in business analysis!

**Salary**

According to Indeed, the average salary for business analysts is $80,615 per year in Ann Arbor, MI.

**Skills required**

*	Bachelor’s Degree or higher in business analysis, business administration, finance, or related field.
*	Excellent written and verbal communication skills.
*	Great analytical, critical thinking and problem-solving abilities.
*	Strong management and organizational skills.
*	Adaptable and capable of working in fast-paced environment. 


```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Business Analyst',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```


## Data Analyst {-#data-analyst}

**Summary of role**

Data analysts are responsible for collecting, storing, and processing a large amounts of data using scientific principles and technical expertise.  They use data to do analysis, make proper decisions, and provide high-quality service for customers. Data Analysts are similar to Business Analysts, however, data analysts are more focused on developing technical skills and using data management and machine learning to construct data structures and dive into data to solve problems.

**Salary**

Here is the overall career path and salary (median) of each path of a Data Analyst:

* Data Analyst (0-1 years): $62,382

* Senior Data Analyst (2-4 years): $95,304

* Senior Data Analyst IV (5-7 years): $128,321

* Principal Data Analyst (8+ years): $143,837

Resource: Glassdoor


**Skills required**

* Master or above degree in Computer Science, Information Management, Data Analysis, and other related.

* Proficient at least one in Java, C++, SQL, Python, R, and other programming language.

* Proficient at least one in Tableau, Qlik, Power BI, and other visualization tools.

* Sensitivity in data mining, processing, and presenting, and willingness to learn new and advanced technical analysis methods.

* Analytical skills to define problems, collect necessary data, establish facts, and provide reasonable recommendations for clients.

* Solid team-working and multi-tasking skills.


**Open roles on LinkedIn**

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Data Analyst',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```

## Business Intelligence Engineer {-#business-intelligence-engineer}

**Summary**

Business intelligence engineers design and build BI tools and systems that are used to collect and analyze data.  Some of these popular BI tools include Qlik, Power BI, and Tablaeu.  These tools help BI engineers present the data and visualizations to the end users.  They also utilize cloud-based data warehousing platforms such as AWS and Snowflake when building models and querying data

They work closely with business stakeholders to create the stories that drive BI development.  These BI tools can be powerful in helping key business members make decisions using timely and accurate data.

BI engineers may also provide training for other staff members on the use of BI tools and programs.

**Salary**

According to [Glassdoor](https://www.glassdoor.com/Career/bi-engineer-career_KO0,11.htm), a BI engineer makes on average $115,400/yr.  This includes $99,050 in base pay and $16,350 in additional pay.

Salaries typically range between $88k and $162k depending on the industry and level of experience.

**Preferred Skills**

* Having a Bachelor's or Graduate's Degree in a technical field such as computer science, engineering, mathematics is often required
* Database experience with SQL or related systems is a must
* Development experience with Python or R
* Being a problem solver and critical thinker
* Familiar with version control and relational databases

**Open roles on LinkedIn**

```{r echo=FALSE}
Job_Postings[Job_Postings$Role=='Business Intelligence Engineer',] %>%
  cards(
    title = Title,
    text = Text,
    link = Link,
    image = Image,
    width = 4,
    border_radius = 5,
    layout = "label-right"
  )
```


<!--chapter:end:03-PossibleCareers.Rmd-->

# Resources {-#resources}

Helpful links for Python, SQL, EXCEL, and other skills required for the relevant jobs

<!--chapter:end:04-Resources.Rmd-->



```{r include=FALSE}
library(readr)
library(knitr)
library(DT)
library(tidyverse)
Job_Postings <- read_csv("assets/company_database.csv")
```


# Company Database {-#company-database}

We wrote a web scraper in Python to pull company data from [Glassdoor](https://www.glassdoor.com/member/home/index.htm).  You can find the code for the scraper on [GitHub](https://github.com/gthuiz/GlassdoorWebScraper). Below are relevant companies by industry that are hiring people for data oriented positions!

```{r echo=FALSE}
Job_Postings = Job_Postings %>%
  mutate(Company =  paste0('<a  target=_blank href=', `Jobs Link`, '>', Company,'</a>' ))


datatable( Job_Postings[c(1,2,9,3)]
  ,rownames = FALSE
 ,escape = F
 ,extensions = c("SearchPanes", "Select", "Buttons")
 ,options = list(
    dom = "Btip",
    buttons = list("searchPanes"),
    
    language = list(searchPanes = list(collapse = "Filter Rows")),
    columnDefs = list(
      list(searchPanes = list(controls = FALSE), targets = 0:2),
      list(className = "dt-center", targets = 0:2),
      list(searchPanes = list(show = FALSE), targets = 3:3)
      )
    )
)

```

<!--chapter:end:05-CompanyDatabase.Rmd-->

# About Us {-#about-us}

## Overview {-#overview}

Our group wants to create a site that highlights everything a MBAn student at Ross should know about the prospective job market.  This includes possible careers they might want to pursue, salary expectations, and companies/cities they might end up in.

## The Team {-#the-team}

***

```{r include=FALSE}
library(readr)
library(knitr)
library(bs4cards)
Team_Bios <- read_csv("assets/Team Bios.csv")
```



```{r include=FALSE}
out = NULL
users = Team_Bios$Title
for (user in users){
  user_data = Team_Bios[Team_Bios$Title==user,]
  out = c(out,knit_expand('templates/about_me_template.Rmd'))
}
```
`r paste(knit(text = out), collapse = '\n')`


<!--chapter:end:06-AboutUs.Rmd-->

